AggregateCounts

### 2021-09-09 R/AggregateCounts.Rmd
Finished stats and sent to Marvin

tTestFigs1ABData<-list(PaWtonovsCoBiomassTtest,PaWtonovsCoAggsTtest,PaWtCoEdgevsCoreBiomassTtest,PaWtCoEdgevsCoreAggsTtest,
                       SaWtonovsCoBiomassTtest,SaWtonovsCoAggsTtest,SaWtCoEdgevsCoreBiomassTtest,SaWtCoEdgevsCoreAggsTtest)
tTestFigs1ABTable<-bind_rows(map(tTestFigs1ABData, TtestTable))
##co wt vs mutants
###Biomass and Aggs of Pa wt vs mutants
PaBiomassAov <- aov(biomass ~ Strain, data = aggregateListSummaryReplicate %>% 
                           filter(Species == "P. aeruginosa" & TimePoint == "Day 4", Culture == "co"))
PaAggsAov <- aov(Aggs ~ Strain, data = aggregateListSummaryReplicate %>% 
                           filter(Species == "P. aeruginosa" & TimePoint == "Day 4", Culture == "co"))
###Biomass and Aggs of Sa wt vs mutants
SaBiomassAov <- aov(biomass ~ Strain, data = aggregateListSummaryReplicate %>% 
                           filter(Species == "S. aureus" & TimePoint == "Day 4", Culture == "co"))
SaAggsAov <- aov(Aggs ~ Strain, data = aggregateListSummaryReplicate %>% 
                           filter(Species == "S. aureus" & TimePoint == "Day 4", Culture == "co"))
summary(PaAggsAov)
TukeyHSD(PaAggsAov)#wt~pqsL p = 0.06, wt~phz p = 0.003
summary(SaAggsAov)
TukeyHSD(SaAggsAov)#wt~pqsL p = 0.03

@@

#Stats for aggregates
##Mono vs Co
PaMono5<-HistReplicateSummary %>% filter(Species == "P. aeruginosa" & TimePoint == "Day 4", Strain == "wt", Culture == "mono",LogBin == "(.5, 5]")
PaCo5<-HistReplicateSummary %>% filter(Species == "P. aeruginosa" & TimePoint == "Day 4", Strain == "wt", Culture == "co",LogBin == "(.5, 5]")
PaMono10<-HistReplicateSummary %>% filter(Species == "P. aeruginosa" & TimePoint == "Day 4", Strain == "wt", Culture == "mono",LogBin == "(5, 10]")
PaCo10<-HistReplicateSummary %>% filter(Species == "P. aeruginosa" & TimePoint == "Day 4", Strain == "wt", Culture == "co",LogBin == "(5, 10]")
PaMono100<-HistReplicateSummary %>% filter(Species == "P. aeruginosa" & TimePoint == "Day 4", Strain == "wt", Culture == "mono",LogBin == "(10, 100]")
PaCo100<-HistReplicateSummary %>% filter(Species == "P. aeruginosa" & TimePoint == "Day 4", Strain == "wt", Culture == "co",LogBin == "(10, 100]")

@@

tTestFigs1CDData<-list(PaMonoCo5BiomassTtest,PaMonoCo5FreqTtest,PaMonoCo10FreqTtest,PaMonoCo100FreqTtest,
                       SaMonoCo5BiomassTtest,SaMonoCo5FreqTtest,SaMonoCo10FreqTtest,SaMonoCo100FreqTtest)
tTestFigs1CDTable<-bind_rows(map(tTestFigs1CDData, TtestTable))
### Edge vs Core
Pawt5E<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint=="Day 4",Strain == "wt", Culture == "co",LogBin == "(.5, 5]",Region == "edge")
Pawt5C<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint== "Day 4",Strain == "wt",Culture == "co",LogBin == "(.5, 5]",Region == "core")
Pawt10E<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint== "Day 4",Strain== "wt",Culture == "co",LogBin == "(5, 10]",Region == "edge")
Pawt10C<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint== "Day 4",Strain== "wt",Culture == "co",LogBin == "(5, 10]",Region == "core")
Pawt100E<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint== "Day 4",Strain=="wt",Culture=="co",LogBin == "(10, 100]",Region == "edge")
Pawt100C<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint== "Day 4",Strain=="wt",Culture=="co",LogBin == "(10, 100]",Region == "core")

@@

tTestFigs2ABDataCorEdge<-list(Pawt5CorEdBioTtest,Pawt5CorEdFreqTtest,Pawt10CorEdFreqTtest,Pawt100CorEdFreqTtest,
                       Sawt5CorEdBioTtest,Sawt5CorEdFreqTtest,Sawt10CorEdFreqTtest,Sawt100CorEdFreqTtest)

tTestFigs2ABTableCorEdge<-bind_rows(map(tTestFigs2ABDataCorEdge, TtestTable))

@@

summary(Pabiomass5Aov)
TukeyHSD(Pabiomass5Aov)
# Summary of the analysis
summary(Sabiomass5Aov)#*p = 0.07
TukeyHSD(Sabiomass5Aov)#*p pqsL-wt 0.077
summary(Safrequency10Aov)#*p = 0.005
TukeyHSD(Safrequency10Aov)#*p pqsL-wt 0.003

#now compute comparison edge vs core
PaPhz5E<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint=="Day 4",Strain == "phz", Culture == "co",LogBin == "(.5, 5]",Region == "edge")
PaPhz5C<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint== "Day 4",Strain == "phz",Culture == "co",LogBin == "(.5, 5]",Region == "core")
PaPhz10E<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint== "Day 4",Strain== "phz",Culture == "co",LogBin == "(5, 10]",Region == "edge")
PaPhz10C<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint== "Day 4",Strain== "phz",Culture == "co",LogBin == "(5, 10]",Region == "core")
PaPhz100E<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint== "Day 4",Strain=="phz",Culture=="co",LogBin == "(10, 100]",Region == "edge")
PaPhz100C<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint== "Day 4",Strain=="phz",Culture=="co",LogBin == "(10, 100]",Region == "core")
PaPqsL5E<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint== "Day 4",Strain=="pqsL",Culture == "co",LogBin == "(.5, 5]",Region == "edge")
PaPqsL5C<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint== "Day 4",Strain=="pqsL",Culture == "co",LogBin == "(.5, 5]",Region == "core")
PaPqsL10E<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint=="Day 4",Strain=="pqsL",Culture == "co",LogBin == "(5, 10]",Region == "edge")
PaPqsL10C<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint=="Day 4",Strain =="pqsL",Culture =="co",LogBin == "(5, 10]",Region == "core")
PaPqsL100E<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint=="Day 4",Strain=="pqsL",Culture=="co",LogBin =="(10, 100]",Region == "edge")
PaPqsL100C<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint== "Day 4",Strain=="pqsL",Culture=="co",LogBin=="(10, 100]",Region == "core")

PaPhz5CorEdBioTtest     <-t.test(x = PaPhz5E$NormalizedBiomass, y = PaPhz5C$NormalizedBiomass, paired = F)
PaPhz5CorEdFreqTtest    <-t.test(x = PaPhz5E$NormalizedFrequency, y = PaPhz5C$NormalizedFrequency, paired = F)
PaPhz10CorEdFreqTtest   <-t.test(x = PaPhz10E$NormalizedFrequency, y = PaPhz10C$NormalizedFrequency, paired = F)
PaPhz100CorEdFreqTtest  <-t.test(x = PaPhz100E$NormalizedFrequency, y = PaPhz100C$NormalizedFrequency, paired = F)
PaPqsL5CorEdBioTtest     <-t.test(x = PaPqsL5E$NormalizedBiomass, y = PaPqsL5C$NormalizedBiomass, paired = F)
PaPqsL5CorEdFreqTtest    <-t.test(x = PaPqsL5E$NormalizedFrequency, y = PaPqsL5C$NormalizedFrequency, paired = F)
PaPqsL10CorEdFreqTtest   <-t.test(x = PaPqsL10E$NormalizedFrequency, y = PaPqsL10C$NormalizedFrequency, paired = F)
PaPqsL100CorEdFreqTtest  <-t.test(x = PaPqsL100E$NormalizedFrequency, y = PaPqsL100C$NormalizedFrequency, paired = F)

SaPhz5E<-HistReplicateSummary %>% filter(Species == "S. aureus" & TimePoint == "Day 4", Strain == "phz", Culture=="co",LogBin =="(.5, 5]",Region == "edge")
SaPhz5C<-HistReplicateSummary %>% filter(Species == "S. aureus" & TimePoint == "Day 4", Strain == "phz", Culture=="co",LogBin =="(.5, 5]",Region == "core")                                        
SaPqsL5E<-HistReplicateSummary %>% filter(Species == "S. aureus" & TimePoint == "Day 4", Strain == "pqsL", Culture == "co",LogBin == "(.5, 5]",Region == "edge")
SaPqsL5C<-HistReplicateSummary %>% filter(Species == "S. aureus" & TimePoint == "Day 4", Strain == "pqsL", Culture == "co",LogBin == "(.5, 5]",Region == "core")
SaPhz10E<-HistReplicateSummary %>% filter(Species == "S. aureus" & TimePoint == "Day 4", Strain == "phz", Culture == "co",LogBin == "(5, 10]",Region == "edge")
SaPhz10C<-HistReplicateSummary %>% filter(Species == "S. aureus" & TimePoint == "Day 4", Strain == "phz", Culture == "co",LogBin == "(5, 10]",Region == "core")
SaPqsL10E<-HistReplicateSummary %>% filter(Species == "S. aureus" & TimePoint == "Day 4", Strain == "pqsL", Culture == "co",LogBin == "(5, 10]",Region == "edge")
SaPqsL10C<-HistReplicateSummary %>% filter(Species == "S. aureus" & TimePoint == "Day 4", Strain == "pqsL", Culture == "co",LogBin == "(5, 10]",Region == "core")
SaPhz100E<-HistReplicateSummary %>% filter(Species == "S. aureus" & TimePoint == "Day 4", Strain == "phz", Culture == "co",LogBin == "(10, 100]",Region == "edge")
SaPhz100C<-HistReplicateSummary %>% filter(Species == "S. aureus" & TimePoint == "Day 4", Strain == "phz", Culture == "co",LogBin == "(10, 100]",Region == "core")
SaPqsL100E<-HistReplicateSummary %>% filter(Species == "S. aureus" & TimePoint == "Day 4", Strain == "pqsL", Culture == "co",LogBin == "(10, 100]",Region == "edge")
SaPqsL100C<-HistReplicateSummary %>% filter(Species == "S. aureus" & TimePoint == "Day 4", Strain == "pqsL", Culture == "co",LogBin == "(10, 100]",Region == "core")
SaPhz5CorEdBioTtest     <-t.test(x = SaPhz5E$NormalizedBiomass, y = SaPhz5C$NormalizedBiomass, paired = F)
SaPhz5CorEdFreqTtest    <-t.test(x = SaPhz5E$NormalizedFrequency, y = SaPhz5C$NormalizedFrequency, paired = F)
SaPhz10CorEdFreqTtest   <-t.test(x = SaPhz10E$NormalizedFrequency, y = SaPhz10C$NormalizedFrequency, paired = F)
SaPhz100CorEdFreqTtest  <-t.test(x = SaPhz100E$NormalizedFrequency, y = SaPhz100C$NormalizedFrequency, paired = F)
SaPqsL5CorEdBioTtest     <-t.test(x = SaPqsL5E$NormalizedBiomass, y = SaPqsL5C$NormalizedBiomass, paired = F)
SaPqsL5CorEdFreqTtest    <-t.test(x = SaPqsL5E$NormalizedFrequency, y = SaPqsL5C$NormalizedFrequency, paired = F)
SaPqsL10CorEdFreqTtest   <-t.test(x = SaPqsL10E$NormalizedFrequency, y = SaPqsL10C$NormalizedFrequency, paired = F)
SaPqsL100CorEdFreqTtest  <-t.test(x = SaPqsL100E$NormalizedFrequency, y = SaPqsL100C$NormalizedFrequency, paired = F)

@@

tTestFigs2CDTable<-bind_rows(map(tTestFigs2CDData, TtestTable))

@@

>>>>

tTestFigs1ABData<-list(PaWtonovsCoBiomassTtest,PaWtonovsCoAggsTtest,PaWtCoEdgevsCoreBiomassTtest,PaWtCoEdgevsCoreAggsTtest,
                       SaWtonovsCoBiomassTtest,SaWtonovsCoAggsTtest,SaWtCoEdgevsCoreBiomassTtest,SaWtCoEdgevsCoreAggsTtest)
tTestFigs1ABTable<-bind_rows(map(tTestFigs1ABData, TtestTable))
##co wt vs mutants
###Biomass and Aggs of Pa wt vs mutants
PaBiomassAov <- aov(biomass ~ Strain, data = aggregateListSummaryReplicate %>% 
                           filter(Species == "P. aeruginosa" & TimePoint == "Day 4", Culture == "co"))
PaAggsAov <- aov(Aggs ~ Strain, data = aggregateListSummaryReplicate %>% 
                           filter(Species == "P. aeruginosa" & TimePoint == "Day 4", Culture == "co"))
###Biomass and Aggs of Sa wt vs mutants
SaBiomassAov <- aov(biomass ~ Strain, data = aggregateListSummaryReplicate %>% 
                           filter(Species == "S. aureus" & TimePoint == "Day 4", Culture == "co"))
SaAggsAov <- aov(Aggs ~ Strain, data = aggregateListSummaryReplicate %>% 
                           filter(Species == "S. aureus" & TimePoint == "Day 4", Culture == "co"))
summary(PaAggsAov)
TukeyHSD(PaAggsAov)#wt~pqsL p = 0.06, wt~phz p = 0.003
summary(SaAggsAov)
TukeyHSD(SaAggsAov)#wt~pqsL p = 0.03
###Core vs edge within mutants
PaPqsLmassE<-aggregateListSummaryReplicate %>% filter(Species =="P. aeruginosa",TimePoint =="Day 4",Strain == "pqsL",Culture == "co",Region == "edge")
PaPqsLmassC<-aggregateListSummaryReplicate %>% filter(Species =="P. aeruginosa",TimePoint =="Day 4",Strain == "pqsL",Culture == "co",Region == "core")
PaPhzmassE<-aggregateListSummaryReplicate %>% filter(Species == "P. aeruginosa",TimePoint =="Day 4",Strain == "phz",Culture == "co",Region == "edge")
PaPhzmassC<-aggregateListSummaryReplicate %>% filter(Species == "P. aeruginosa",TimePoint =="Day 4",Strain == "phz",Culture == "co",Region == "core")

SaPqsLmassE<-aggregateListSummaryReplicate %>% filter(Species =="S. aureus",TimePoint =="Day 4",Strain == "pqsL",Culture == "co",Region == "edge")
SaPqsLmassC<-aggregateListSummaryReplicate %>% filter(Species =="S. aureus",TimePoint =="Day 4",Strain == "pqsL",Culture == "co",Region == "core")
SaPhzmassE<-aggregateListSummaryReplicate %>% filter(Species == "S. aureus",TimePoint =="Day 4",Strain == "phz",Culture == "co",Region == "edge")
SaPhzmassC<-aggregateListSummaryReplicate %>% filter(Species == "S. aureus",TimePoint =="Day 4",Strain == "phz",Culture == "co",Region == "core")

PaPqsLCoEdgevsCoreBiomassTtest<-t.test(x = PaPqsLmassE$biomass, y = PaPqsLmassC$biomass, paired = F)
PaPqsLCoEdgevsCoreAggsTtest<-t.test(x = PaPqsLmassE$Aggs, y = PaPqsLmassC$Aggs, paired = F)
PaPhzCoEdgevsCoreBiomassTtest<-t.test(x = PaPhzmassE$biomass, y = PaPhzmassC$biomass, paired = F)
PaPhzCoEdgevsCoreAggsTtest<-t.test(x = PaPhzmassE$Aggs, y = PaPhzmassC$Aggs, paired = F)

SaPqsLCoEdgevsCoreBiomassTtest<-t.test(x = SaPqsLmassE$biomass, y = SaPqsLmassC$biomass, paired = F)
SaPqsLCoEdgevsCoreAggsTtest<-t.test(x = SaPqsLmassE$Aggs, y = SaPqsLmassC$Aggs, paired = F)
SaPhzCoEdgevsCoreBiomassTtest<-t.test(x = SaPhzmassE$biomass, y = SaPhzmassC$biomass, paired = F)
SaPhzCoEdgevsCoreAggsTtest<-t.test(x = SaPhzmassE$Aggs, y = SaPhzmassC$Aggs, paired = F)

tTestFigs2ABDataCvsE<-list(PaPqsLCoEdgevsCoreBiomassTtest,PaPqsLCoEdgevsCoreAggsTtest,PaPhzCoEdgevsCoreBiomassTtest,PaPhzCoEdgevsCoreAggsTtest,
                           SaPqsLCoEdgevsCoreBiomassTtest,SaPqsLCoEdgevsCoreAggsTtest,SaPhzCoEdgevsCoreBiomassTtest,SaPhzCoEdgevsCoreAggsTtest)
tTestFigs2ABTableCvsE<-bind_rows(map(tTestFigs1ABDataCvsE, TtestTable))

@@

#Stats for aggregate frequency and biomass
#####
##Mono vs Co
###
PaMono5<-HistReplicateSummary %>% filter(Species == "P. aeruginosa" & TimePoint == "Day 4", Strain == "wt", Culture == "mono",LogBin == "(.5, 5]")
PaCo5<-HistReplicateSummary %>% filter(Species == "P. aeruginosa" & TimePoint == "Day 4", Strain == "wt", Culture == "co",LogBin == "(.5, 5]")
PaMono10<-HistReplicateSummary %>% filter(Species == "P. aeruginosa" & TimePoint == "Day 4", Strain == "wt", Culture == "mono",LogBin == "(5, 10]")
PaCo10<-HistReplicateSummary %>% filter(Species == "P. aeruginosa" & TimePoint == "Day 4", Strain == "wt", Culture == "co",LogBin == "(5, 10]")
PaMono100<-HistReplicateSummary %>% filter(Species == "P. aeruginosa" & TimePoint == "Day 4", Strain == "wt", Culture == "mono",LogBin == "(10, 100]")
PaCo100<-HistReplicateSummary %>% filter(Species == "P. aeruginosa" & TimePoint == "Day 4", Strain == "wt", Culture == "co",LogBin == "(10, 100]")

@@

tTestFigs1CDData<-list(PaMonoCo5BiomassTtest,PaMonoCo5FreqTtest,PaMonoCo10FreqTtest,PaMonoCo100FreqTtest,
                       SaMonoCo5BiomassTtest,SaMonoCo5FreqTtest,SaMonoCo10FreqTtest,SaMonoCo100FreqTtest)
tTestFigs1CDTable<-bind_rows(map(tTestFigs1CDData, TtestTable))
### Edge vs Core only co-cultures
#####
Pawt5E<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint=="Day 4",Strain == "wt", Culture == "co",LogBin == "(.5, 5]",Region == "edge")
Pawt5C<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint== "Day 4",Strain == "wt",Culture == "co",LogBin == "(.5, 5]",Region == "core")
Pawt10E<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint== "Day 4",Strain== "wt",Culture == "co",LogBin == "(5, 10]",Region == "edge")
Pawt10C<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint== "Day 4",Strain== "wt",Culture == "co",LogBin == "(5, 10]",Region == "core")
Pawt100E<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint== "Day 4",Strain=="wt",Culture=="co",LogBin == "(10, 100]",Region == "edge")
Pawt100C<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint== "Day 4",Strain=="wt",Culture=="co",LogBin == "(10, 100]",Region == "core")

@@

tTestFigs1CDDataCorEdge<-list(Pawt5CorEdBioTtest,Pawt5CorEdFreqTtest,Pawt10CorEdFreqTtest,Pawt100CorEdFreqTtest,
                       Sawt5CorEdBioTtest,Sawt5CorEdFreqTtest,Sawt10CorEdFreqTtest,Sawt100CorEdFreqTtest)

tTestFigs1CDTableCorEdge<-bind_rows(map(tTestFigs1CDDataCorEdge, TtestTable))

@@

# Summary of the analysis #only showing significant values
summary(Sabiomass5Aov)#*p = 0.07
TukeyHSD(Sabiomass5Aov)#*p pqsL-wt 0.077
summary(Safrequency10Aov)#*p = 0.005
TukeyHSD(Safrequency10Aov)#*p pqsL-wt 0.003

#bundling up bin and edge
HistReplicateSummary$StrainRegion <- paste(HistReplicateSummary$Region, "-", HistReplicateSummary$Strain)

Pabiomass5AovSR <- aov(NormalizedBiomass ~ StrainRegion, data = HistReplicateSummary%>%
                     filter(Species == "P. aeruginosa",TimePoint == "Day 4",Culture == "co",LogBin == "(.5, 5]"))
Pafrequency5AovSR <- aov(NormalizedFrequency ~ StrainRegion, data = HistReplicateSummary%>%
                       filter(Species == "P. aeruginosa",TimePoint == "Day 4",Culture == "co",LogBin == "(.5, 5]"))
Pafrequency10AovSR <- aov(NormalizedFrequency ~ StrainRegion, data = HistReplicateSummary%>%
                       filter(Species == "P. aeruginosa",TimePoint == "Day 4",Culture == "co",LogBin == "(5, 10]"))
Pafrequency100AovSR <- aov(NormalizedFrequency ~ StrainRegion, data = HistReplicateSummary%>%
                       filter(Species == "P. aeruginosa",TimePoint == "Day 4",Culture == "co",LogBin == "(10, 100]"))
##None of the Pa are significant
Sabiomass5AovSR <- aov(NormalizedBiomass ~ StrainRegion, data = HistReplicateSummary%>%
                     filter(Species == "S. aureus",TimePoint == "Day 4",Culture == "co",LogBin == "(.5, 5]")) 
Safrequency5AovSR <- aov(NormalizedFrequency ~ StrainRegion, data = HistReplicateSummary%>%
                       filter(Species == "S. aureus",TimePoint == "Day 4",Culture == "co",LogBin == "(.5, 5]"))
Safrequency10AovSR <- aov(NormalizedFrequency ~ StrainRegion, data = HistReplicateSummary%>%
                       filter(Species == "S. aureus",TimePoint == "Day 4",Culture == "co",LogBin == "(5, 10]"))
Safrequency100AovSR <- aov(NormalizedFrequency ~ StrainRegion, data = HistReplicateSummary%>%
                       filter(Species == "S. aureus",TimePoint == "Day 4",Culture == "co",LogBin == "(10, 100]"))
summary(Sabiomass5AovSR)#
TukeyHSD(Sabiomass5AovSR)#*p core wt vs core pqsL 0.08, edge phz vs core pqsL 0.04, edge wt core pqsL .08
summary(Safrequency5AovSR)# nope
summary(Safrequency10AovSR)#yup
TukeyHSD(Safrequency10AovSR)# core pqsL VS core wt 0.01, vs edge phz 0.03 edge pqsL 0.06, edge wt 0.03 
summary(Safrequency100AovSR)

#now compute comparison edge vs core
##Pa
PaPhz5E<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint=="Day 4",Strain == "phz", Culture == "co",LogBin == "(.5, 5]",Region == "edge")
PaPhz5C<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint== "Day 4",Strain == "phz",Culture == "co",LogBin == "(.5, 5]",Region == "core")
PaPhz10E<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint== "Day 4",Strain== "phz",Culture == "co",LogBin == "(5, 10]",Region == "edge")
PaPhz10C<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint== "Day 4",Strain== "phz",Culture == "co",LogBin == "(5, 10]",Region == "core")
PaPhz100E<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint== "Day 4",Strain=="phz",Culture=="co",LogBin == "(10, 100]",Region == "edge")
PaPhz100C<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint== "Day 4",Strain=="phz",Culture=="co",LogBin == "(10, 100]",Region == "core")
PaPqsL5E<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint== "Day 4",Strain=="pqsL",Culture == "co",LogBin == "(.5, 5]",Region == "edge")
PaPqsL5C<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint== "Day 4",Strain=="pqsL",Culture == "co",LogBin == "(.5, 5]",Region == "core")
PaPqsL10E<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint=="Day 4",Strain=="pqsL",Culture == "co",LogBin == "(5, 10]",Region == "edge")
PaPqsL10C<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint=="Day 4",Strain =="pqsL",Culture =="co",LogBin == "(5, 10]",Region == "core")
PaPqsL100E<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint=="Day 4",Strain=="pqsL",Culture=="co",LogBin =="(10, 100]",Region == "edge")
PaPqsL100C<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint== "Day 4",Strain=="pqsL",Culture=="co",LogBin=="(10, 100]",Region == "core")

PaPhz5CorEdBioTtest     <-t.test(x = PaPhz5E$NormalizedBiomass, y = PaPhz5C$NormalizedBiomass, paired = F)
PaPhz5CorEdFreqTtest    <-t.test(x = PaPhz5E$NormalizedFrequency, y = PaPhz5C$NormalizedFrequency, paired = F)
PaPhz10CorEdFreqTtest   <-t.test(x = PaPhz10E$NormalizedFrequency, y = PaPhz10C$NormalizedFrequency, paired = F)
PaPhz100CorEdFreqTtest  <-t.test(x = PaPhz100E$NormalizedFrequency, y = PaPhz100C$NormalizedFrequency, paired = F)
PaPqsL5CorEdBioTtest     <-t.test(x = PaPqsL5E$NormalizedBiomass, y = PaPqsL5C$NormalizedBiomass, paired = F)
PaPqsL5CorEdFreqTtest    <-t.test(x = PaPqsL5E$NormalizedFrequency, y = PaPqsL5C$NormalizedFrequency, paired = F)
PaPqsL10CorEdFreqTtest   <-t.test(x = PaPqsL10E$NormalizedFrequency, y = PaPqsL10C$NormalizedFrequency, paired = F)
PaPqsL100CorEdFreqTtest  <-t.test(x = PaPqsL100E$NormalizedFrequency, y = PaPqsL100C$NormalizedFrequency, paired = F)
##Sa
SaPhz5E<-HistReplicateSummary %>% filter(Species == "S. aureus" & TimePoint == "Day 4", Strain == "phz", Culture=="co",LogBin =="(.5, 5]",Region == "edge")
SaPhz5C<-HistReplicateSummary %>% filter(Species == "S. aureus" & TimePoint == "Day 4", Strain == "phz", Culture=="co",LogBin =="(.5, 5]",Region == "core")                                        
SaPqsL5E<-HistReplicateSummary %>% filter(Species == "S. aureus" & TimePoint == "Day 4", Strain == "pqsL", Culture == "co",LogBin == "(.5, 5]",Region == "edge")
SaPqsL5C<-HistReplicateSummary %>% filter(Species == "S. aureus" & TimePoint == "Day 4", Strain == "pqsL", Culture == "co",LogBin == "(.5, 5]",Region == "core")
SaPhz10E<-HistReplicateSummary %>% filter(Species == "S. aureus" & TimePoint == "Day 4", Strain == "phz", Culture == "co",LogBin == "(5, 10]",Region == "edge")
SaPhz10C<-HistReplicateSummary %>% filter(Species == "S. aureus" & TimePoint == "Day 4", Strain == "phz", Culture == "co",LogBin == "(5, 10]",Region == "core")
SaPqsL10E<-HistReplicateSummary %>% filter(Species == "S. aureus" & TimePoint == "Day 4", Strain == "pqsL", Culture == "co",LogBin == "(5, 10]",Region == "edge")
SaPqsL10C<-HistReplicateSummary %>% filter(Species == "S. aureus" & TimePoint == "Day 4", Strain == "pqsL", Culture == "co",LogBin == "(5, 10]",Region == "core")
SaPhz100E<-HistReplicateSummary %>% filter(Species == "S. aureus" & TimePoint == "Day 4", Strain == "phz", Culture == "co",LogBin == "(10, 100]",Region == "edge")
SaPhz100C<-HistReplicateSummary %>% filter(Species == "S. aureus" & TimePoint == "Day 4", Strain == "phz", Culture == "co",LogBin == "(10, 100]",Region == "core")
SaPqsL100E<-HistReplicateSummary %>% filter(Species == "S. aureus" & TimePoint == "Day 4", Strain == "pqsL", Culture == "co",LogBin == "(10, 100]",Region == "edge")
SaPqsL100C<-HistReplicateSummary %>% filter(Species == "S. aureus" & TimePoint == "Day 4", Strain == "pqsL", Culture == "co",LogBin == "(10, 100]",Region == "core")
SaPhz5CorEdBioTtest     <-t.test(x = SaPhz5E$NormalizedBiomass, y = SaPhz5C$NormalizedBiomass, paired = F)
SaPhz5CorEdFreqTtest    <-t.test(x = SaPhz5E$NormalizedFrequency, y = SaPhz5C$NormalizedFrequency, paired = F)
SaPhz10CorEdFreqTtest   <-t.test(x = SaPhz10E$NormalizedFrequency, y = SaPhz10C$NormalizedFrequency, paired = F)
SaPhz100CorEdFreqTtest  <-t.test(x = SaPhz100E$NormalizedFrequency, y = SaPhz100C$NormalizedFrequency, paired = F)
SaPqsL5CorEdBioTtest     <-t.test(x = SaPqsL5E$NormalizedBiomass, y = SaPqsL5C$NormalizedBiomass, paired = F)
SaPqsL5CorEdFreqTtest    <-t.test(x = SaPqsL5E$NormalizedFrequency, y = SaPqsL5C$NormalizedFrequency, paired = F)
SaPqsL10CorEdFreqTtest   <-t.test(x = SaPqsL10E$NormalizedFrequency, y = SaPqsL10C$NormalizedFrequency, paired = F)
SaPqsL100CorEdFreqTtest  <-t.test(x = SaPqsL100E$NormalizedFrequency, y = SaPqsL100C$NormalizedFrequency, paired = F)

@@

tTestFigs2CDTableCorevsEdge<-bind_rows(map(tTestFigs2CDData, TtestTable))

@@

plankAggHistRepStats<-plankAggHistRep %>%
  group_by(Species,SaStrain,Strain,Culture,TimePoint,Condition,Aggregation)%>%
  summarize(MeanFreq = mean(AgPlNormFrequency), MeanBiomass = mean(AgPlNormBiomass))
